\documentclass[11pt]{extarticle}
\usepackage[tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{float}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{ragged2e}
\usepackage{titlesec}
\usepackage{framed}
\usepackage{color}   %May be necessary if you want to color links
\usepackage{hyperref}
\usepackage{footnotebackref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{pgfplots}
\usepackage{lscape}
\pgfplotsset{tick label style={font=\tiny}}

\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=section,     %set to all if you want both sections and subsections linked
    linkcolor=black,  %choose some color if you want links to stand out
}

\fancypagestyle{myheadings}
{
    \fancyhf{}
    \renewcommand{\footrulewidth}{0pt}
    \renewcommand{\headrulewidth}{0pt}
    \cfoot{Page \thepage\ of \pageref*{LastPage}}    
}

\fancypagestyle{plain}
{
    \fancyhf{}
    \chead{\small Project Proposal}
    \lhead{\small CS 353}
    \rhead{\small Spring 2022}
    % \renewcommand{\footrulewidth}{0.5pt}
    \renewcommand{\headrulewidth}{0.5pt}
    \cfoot{Page \thepage\ of \pageref*{LastPage}}    
}

\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{CStyle}{
    backgroundcolor=\color{backgroundColour},
    % backgroundcolor = \color{white},   
    commentstyle=\color{mGreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{mGray},
    stringstyle=\color{mPurple},
    basicstyle=\footnotesize\bfseries\fontfamily{cmtt}\selectfont,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    frame = single,
    language=C
}

\title{\textbf{Project Proposal}}
\author{Aliza Rafique (05986); Asad Tariq (05439); Fahad Shaikh (05452)}
\date{$3^{rd}$ February 2022}


% Set formats for each heading level
\titleformat*{\section}{\Large\bfseries\fontfamily{phv}\selectfont}
\titleformat*{\subsection}{\large\bfseries\fontfamily{phv}\selectfont}
\titleformat*{\subsubsection}{\itshape\subsubsectionfont}

\providecommand\phantomsection{}

\doublespacing
\begin{document}
\input{title_page.tex}
\newpage
\thispagestyle{empty}
\tableofcontents
\newpage
\pagestyle{plain}

\section{Executive Summary}
\noindent
This will be an Android application that will be focused on providing authentic and robust reviews of different businesses (such as restaurants and tech gadgets). It will enable people to make informed choices on what to buy and where to buy from.

\section{Project Scope}
\noindent
This Android application is a “business review” application that will act as a platform for users to review different businesses (restaurants, auto-part mechanics, tech gadgets, etc) and give their opinions. It is an on-the-go application that will help users to make better choices when it comes to locating the best places for their needs, be it a restaurant or a supermarket. Each business featured on the application will have well-curated reviews given by a verified customer of that business, thereby providing other users with authentic information. Each user will be assigned a rating, which will be based upon how many reviews he/she posts of different businesses and also on how many likes he/she gets for them. We hope that, via this application, the people of Karachi can have some sort of metric to choose from the ever-growing vast pool of businesses in all sorts of fields.

\section{Technology Stack}
\subsection{Frontend}
\begin{enumerate}[label={\alph*.}]
    \item Flutter UI toolkit \& libraries
    \item Dart programming language
\end{enumerate}

\subsection{Backend \& Database}
\begin{enumerate}[label={\alph*.}]
    \item MongoDB \textbf{OR} SQLite
    \item HTTP $0.12.2$ library
\end{enumerate}

\section{Server Details}
\begin{enumerate}[label={\alph*.}]
    \item \texttt{Get\_Server} Dart Package
\end{enumerate}

\section{Interfaces}
\subsection{Custom APIs}
\begin{enumerate}[label={\alph*.}]
    \item This API will be used to collect data from the user which will be encrypted in our database and then decrypted data will be shown to the user when requested.
    \item The reviews made by each user will be encrypted.
\end{enumerate}

\subsection{Third Party APIs}
\textbf{Google and Facebook APIs} - This will be used for easy registration:
\begin{enumerate}[label={\alph*.}]
    \item Facebook API limitations: Any individual user can make more than 200 calls per hour using our app, as long as the total calls from our app does not exceed the app maximum.
    For example, if our app has 100 users, our app can make 20,000 calls per hour.
    \item Google API limitations: 50,000 requests per Project per day. By default, it is set to 100 requests per 100 seconds per user and can be adjusted to a maximum value of 1,000. But the number of requests to the API is restricted to a maximum of 10 requests per second per user.
    \item Google Maps API limitation: 28,500 maploads per month, free of charge.
\end{enumerate}

\section{Functional Requirements}
\begin{table}[H]
    \begin{center}
        \begin{tabular}{ |m{6cm}|p{6cm}| } 
           \hline
           \textbf{Features} & \textbf{Description} \\
           \hline
           Login/ Logout / SignUp / Forgot Password & If a user wishes to use the application, he or she requires an account to log in to the application. Option for SignUp is for those who do not have an account. Users who already have an account are required to log in only. The user is given the option of ``Forgot Password” in case the user forgets his or her password. A verification code will be emailed on the email ID to create the password.\\
           \hline
           User Profile & Users have the option to provide their picture, select their gender, provide their date of birth or any notes they would like to tell about.\\
           \hline
           Post a review & The user can post a review in the form of text, pictures, and the location of the place he/she is reviewing. They can also rate the place out of 10.\\
           \hline
           Comment on a review & The user can comment his/her views on an already posted review.\\
           \hline
           Like a review & The user can like a particular review on the app (similar to Instagram).\\
           \hline
           Search for reviews on a particular item & The user will be able to search for reviews previously posted by other users of the application for a particular item of his/her choice.\\
           \hline
           View different categories of items & The user will have the option to browse through different categories of items and choose an item to read through its reviews.\\
           \hline
        \end{tabular}
    \end{center}
    \caption{\label{tab:Table 1} Functional Requirements of the project listed with their descriptions.}
\end{table}

\end{document}
